The Effects of the NBA COVID Bubble on the NBA Playoffs

### 2020-11-10 Manuscript/NBABubbleAnalysis.Rmd
Update NBABubbleAnalysis.Rmd

(ref:cap-Fig2) Shows the home(blue) and away (red) scoring distirbutions for 2020(bottom) and 2017-2019(top)"
```{r Fig2, echo=FALSE, fig.cap="(ref:cap-Fig2)", fig.align='center'}
ggplot(combined) + 
  geom_histogram(aes(x = PTS, y = ..density.., fill = Home.Away), bins = 10, binwidth = 5)+
  facet_grid(Year ~ Home.Away)+
  theme(legend.position = "none")
```

@@

Comparisons between 2020 and 2017-19 home and away teams were made on home team
winning percentage, total team scoring and two-point, three-point and free throw
shooting. Comparing the differences in these metrics for home and away teams in
2020 vs previous years will provide valuable insights to the understanding of 
home-court advantage. We can see how going on the road may negatively impact 
away performance and how playing at home may positively impact home performance.
If there are differences in scoring for home or away teams the differences can
be used to show how home-court advantage affects overall performance of home
and away teams. While testing for differences in shooting will provide added
context for how home-court advantage specifically affects performance. 
Shooting percentages aren’t the only possible metrics affected by home-court
advantage, but they are the most obvious and certainly an important one. In
order to compare these differences simple two-sample z-tests were conducted.
Test for differences in means was conducted for comparing scoring totals, shown in 
Equation \@ref(eq:zmean). Tests for differences in proportions were conducted for
comparing winning percentage and the three different shooting percentages, shown
in Equation \@ref(eq:zprop).

>>>>

(ref:cap-Fig2) Shows the home(blue) and away (red) scoring distributions for 2020(bottom) and 2017-2019(top)"
```{r Fig2, echo=FALSE, fig.cap="(ref:cap-Fig2)", fig.align='center'}
ggplot(combined) + 
  geom_histogram(aes(x = PTS, y = ..density.., fill = Home.Away), bins = 10, binwidth = 5)+
  facet_grid(Year ~ Home.Away)+
  theme(legend.position = "none")
```

@@

Comparisons between 2020 and 2017-19 home and away teams were made on home team
winning percentage, total team scoring and two-point, three-point and free throw
shooting. Comparing the differences in these metrics for home and away teams in
2020 vs previous years will provide valuable insights to the understanding of 
home-court advantage. We can see how going on the road may negatively impact 
away performance and how playing at home may positively impact home performance.
If there are differences in scoring for home or away teams the differences can
be used to show how home-court advantage affects overall performance of home
and away teams. While testing for differences in shooting will provide added
context for how home-court advantage specifically affects performance. 
Shooting percentages aren’t the only possible metrics affected by home-court
advantage, but they are the most obvious and certainly an important one. In
order to compare these differences simple two-sample z-tests were conducted.
Test for differences in means was conducted for comparing scoring totals, shown in 
Equation \@ref(eq:zmean). Tests for differences in proportions were conducted for
comparing winning percentage and the three different shooting percentages, shown
in Equation \@ref(eq:zprop). All 9 tests are conducted under the assumption and null
hypothesis that there should be no difference in statistics from 2020 compared
to those from 2017-2019.
